Beyond query expansion - expanding documents for fluid keyword search

### 2020-10-07 IUI2021/paper.tex
...

To solve the vocabulary problem and the translation problem,
we propose the combination of three techniques.

\begin{itemize}

\item Using ExpandSearch

The main idea for solving the problem is 
providing \textbf{regular expressions} (REs)
for  each document so that a wide variety of user queries can match one of the expanded strings.

When we want to provide a manual that describes how to delete a file, 
we provide a RE like \verb|(delete|remove) (a file|data)|
and generate all the text that match this RE.
In this case, we can epand this RE into
\verb|delete a file|,
\verb|delete data|,
\verb|remove a file|, and
\verb|remove data|.
and use all these strings for the search.
Users can find this document by using fleible query like
\verb|delete file| or
\verb|remove data|.
We can add descriptions in other languages, like \verb|(ファイル|データ)を(消す|(消去|削除)する)|
A user can use a phrase like ``ファイルを消去する'' to find the manual page.

\item Approximate pattern matching

@@

\item Document expansion by users

As we have shown before, one of the big reasons why we fail to find a document is that
the user's search keyword does not exist in the document.
 Providing entries for ExpandHelp can solve the problem, but
If the author of the does not provide the data, it would be nice if other users can add
the ExpandHelp entries.
This strategy is very similar to writing a hands-on document for an existing document,
but adding ExpandHelp entries is much easier than authoring  a document from scratch.

\end{itemize}

@@

\subsection{Helpfeel services}

@@

\begin{verbatim}
 https://paypayfleamarket.yahoo.co.jp/help/
[https://gyazo.com/3d964512606a5e25646104a738ab104e]
\end{verbatim}

>>>>

To solve the vocabulary problem and the translation problem,
we propose the combination of three techniques described below.

\begin{enumerate}

\item \textbf{Using ExpandSearch}

  The main idea for solving the problem is 
  providing \textbf{regular expressions} (REs)
  for  each document so that a wide variety of user queries can match one of the
  strings expanded from the REs.

  When we want to provide a manual that describes how to delete a file, 
  we provide a RE like \verb*(delete|remove) (a file|data)*
  and generate all the text that match this RE.
  In this case, we can epand this RE into
  \verb|delete a file|,
  \verb|delete data|,
  \verb|remove a file|, and
  \verb|remove data|.
  and use all these strings for the search.
  Users can find this document by using fleible query like
  \verb|delete file| or
  \verb|remove data|.
  We can add descriptions in other languages, like \verb*(ファイル|データ)を(消す|(消去|削除)する)*
  A user can use a phrase like ``ファイルを消去する'' to find the manual page.

\item \textbf{Approximate pattern matching}

@@

\item \textbf{Document expansion by users}

  As we have shown before, one of the big reasons why we fail to find a document is that
  the user's search keyword does not exist in the document.
  Providing entries for ExpandSearch can solve the problem, but

  If the author of the document does not provide the data, it would be nice if
  other users can add the ExpandHelp entries.
  This strategy is very similar to writing a hands-on document for an existing document,
  but adding ExpandHelp entries is much easier than authoring  a document from scratch.

\end{enumerate}

@@

\subsection{Helpfeel}

@@

% https://paypayfleamarket.yahoo.co.jp/help/

\begin{figure}[H]
  \centering
  \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
  \caption{PayPay Freemarket}
  \Description{PayPay}
\end{figure}
